\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-11-23 Manuscript/reply.tex
comments on reply
went over referee 1 comments

We extend our gratitude to the Editor and Associate Editor for 
granting us the opportunity to revise this manuscript. We also want to
express our appreciation to the reviewers for their valuable comments.

The manuscript has been revised accordingly with the most notable change being 
the addition of new data in both the GLMM and rank comparison sections in an
attempt to expand the scope of the analysis and derive better insights.

@@

Thank you for your feedback. We have carefully addressed the
reviewers' comments and taken additional steps to streamline the
manuscript, focusing on a clearer presentation of the key goals and
findings from the outset. We appreciate your time and consideration in
re-evaluating our submission.

@@

We thank the reviewer for the accurate summary of our contributions
and these encouraging comments.

@@

Thank you for the valuable suggestions. We have extended our analysis
by including data from both men's and women's 100-meter dash. This was
justified by a GLMM fit to these data and the event type was not found
to be significantly different in reaction time.

We also considered including additional sprinting events such as the
200-meter dash; however, in a GLMM fit to an expanded dataset that
additionally included 200-meter, the event type effect became
significant. Subsequent pairwise comparisons using Tukey’s Honest
Significant Difference (HSD) test revealed a p-value of 0.0021 when
comparing the reaction times of the 200-meter dash and the 110-meter
hurdles, and a p-value of 0.000017 when comparing the 100-meter dash
and the 200-meter dash. These results indicate that reaction times in
the 200-meter dash are significantly slower, suggesting that this
event does not align well with our focus on extreme reaction times.
Consequently, we decided to exclude the 200-meter data from our
primary analysis.

This difference in reaction times is not unexpected, however, as athletes 
competing in longer sprint
events, such as the 200-meter dash, may not prioritize reaction time
as highly as those specializing in shorter sprints like the 100-meter
dash. While it is common for amateur and collegiate athletes to
compete across multiple sprint distances, elite athletes at the World
Championship level may not exhibit equally strong performances in all
sprint events. Our study aims to evaluate the probability of observing
extreme reaction times, particularly in the context of the 0.1-second
threshold. Including data from events with systematically slower
reaction times would artificially inflate the extremity of a
0.1-second reaction time, potentially biasing our conclusions.

@@

We apologize for the confusion. The heat effect actually measures the speed-level 
of the heat, not the type of heat.  We added some additional
explanations in the first paragraph of section 3.2 to make it clear what the
venue and heat effect refer to. We did not want to call it a ``race effect" as we
were worried that may be interpreted to mean the race of the athlete.  We did
not think it would be informative to  add and effect for individual runner's
average ability as many of observations in the data come from runners
\jy{It's the number of runners with 1 data point that determines how
  hard the athlete effect can be estimated. How many runners had only 1
  data point?}
with very few (1-3) data points, so taking an average of such a small sample may
not be informative, especially if there are outliers or an athlete had a bad
start.
\eds{let's revisit this again after objective 2 analyses are set}

@@

We appreciate the feedback, which was echoed by the second
reviewer. To address these concerns, we revised the introduction to
better structure our arguments. We streamlined the literature review
to focus only on studies directly relevant to our analysis and
clarified the paper’s two main objectives: (1) identifying
inconsistencies in the 2022 reaction times and (2) assessing whether
the 0.1-second threshold is fair. We avoided speculating on sensor
calibration or implicating Seiko due to a lack of direct evidence, and
instead, we provide general recommendations for World Athletics while
noting that the unusually fast reaction times in 2022 remain
unexplained.

@@

Thank you for the positive feedback. We expanded both the rank
comparison and the GLMM sections with additional data to strengthen our
analysis. These enhancements support our findings of an anomaly in
2022 and highlight that the 0.1-second reaction time threshold lacks a
foundation in formal statistical evidence.
\eds{let's revisit this again after objective 2 analyses are set}

>>>>

We sincerely thank the Editor and Associate Editor for the opportunity
to revise our manuscript. The insightful comments and constructive
feedback from the reviewers have greatly enhanced the quality of this
work, and we are deeply grateful for their efforts.

The manuscript has been revised accordingly with the following most
notable changes:
\begin{enumerate}
\item
  The focus of the study has been clarified in the completely
  rewritten introduction. The two objectives are 1) to investigate
  whether the reaction times at the 2022 World Championships were
  significantly different from the other competitions; and 2) to
  assess the appropriateness of the 0.1-second threshold.
\item
  Additional data (reaction times from the 100-meter dash) have been
  added to the analysis for both objectives to expand the scope of the
  analysis and derive better insights.
\item
  In the assessment of the 0.1-second threshold, the Gamma GLMM has
  been replaced with a generalized Gamma distributions in the flexible
  framework of Generalized Additive Models for Location, Scale, and
  Shape (GAMLSS) \citep{stasinopoulos2024generalized}, with random
  effects of venue and heat in two of its parameters, respectively.
  The new model provides an adequate fit to the data, as confirmed by
  diagnostic checks.
\end{enumerate}

@@

Thank you for your feedback. As detailed in the summary of notable changes, 
we have thoroughly addressed the reviewers' comments and restructured the 
manuscript to clearly identify its key goals and present the main findings 
concisely. We appreciate your time and consideration in re-evaluating our 
submission.

@@

We thank the reviewer for the accurate summary of our contributions
and for the encouraging feedback. As part of our revisions, we have
expanded the analysis to include reaction times from the 100-meter
dash. Additionally, we replaced the gamma GLMM with a generalized
Gamma distribution in the flexible framework of GAMLSS,  featuring
random effects in its parameters, which provides an improved and
adequate fit to the data.

@@

Thank you for the valuable suggestions. In response, we expanded our
analysis to include reaction time data from both men and women's
100-meter dashes. A generalized gamma model fit to these data showed
no significant differences in reaction times by event type.

We also explored adding data from the 200-meter dash. However, a
generalized gamma model fit to the expanded dataset that included the
200-meter event revealed a significant effect of event type. Tukey’s
Honest Significant Difference (HSD) test found a p-value of 0.0021 for
the 200-meter dash compared to the 110-meter hurdles, and a p-value of
0.000017 for the 100-meter dash compared to the 200-meter dash.
These results indicate that reaction times in the 200-meter dash are
significantly slower. Consequently, we excluded the 200-meter event
from the main analysis, as its systematic differences in reaction
times could bias conclusions about extreme reaction times and the
appropriateness of the 0.1-second threshold.

The observed differences in reaction times between events are not
unexpected. Athletes competing in longer sprints, such as the
200-meter dash, may place less emphasis on reaction time compared to
those in shorter sprints like the 100-meter dash. Elite athletes at
the World Championship level often specialize in specific distances,
and performance across events may vary. Including data from events
with systematically slower reaction times would inflate the extremity
of a 0.1-second reaction time, potentially skewing the results of our
study, which focuses on the likelihood of extreme reaction times
relative to this threshold.

@@

Thank you for this thoughtful suggestion. We apologize for any
confusion regarding the heat effect. In our model, the heat effect
captures the speed-level of the heat rather than the type of heat
(e.g., preliminary vs. final). To clarify this, we have added
additional explanations in the first paragraph of Section~3.2 to
explicitly define the venue and heat effects. We avoided calling it a
``race effect'' to prevent misinterpretation as referring to the
athlete's race.

We considered adding an effect for an individual runner’s average
ability; however, many observations in our dataset come from athletes
with only 1–-3 data points. Taking an average for such small samples
may not be informative, especially in the presence of outliers or
cases where an athlete had an atypical start. As such, we opted not to
include this factor in the model.

In the revision, we replaced the Gamma GLMM with a generalized Gamma
distribution in the GAMLSS framework. The venue effect and heat effect
were incorporated into two parameters controlling the scale of the
distribution. This revised model provides an improved and adequate fit
to the data compared to the original Gamma GLMM.
\eds{let's revisit this again after objective 2 analyses are set}

@@

We appreciate the feedback, which aligns with concerns raised by
Reviewer~2. To address this, we completely rewrote the introduction to
better structure our arguments and focus the problem statements. The
literature review was streamlined to highlight studies directly
relevant to our analysis. We clarified the paper’s two main
objectives: (1) identifying inconsistencies in reaction times at the
2022 World Championships, and (2) assessing the fairness of the
0.1-second threshold.

We avoided speculation about sensor calibration or implicating Seiko,
as there is no direct evidence to support such claims. Instead, we
provide general recommendations for World Athletics while noting that
the unusually fast reaction times observed in 2022 remain unexplained.

@@

Thank you for the positive feedback. We have expanded both the rank
comparison and the GAMLSS model sections with additional data to
strengthen our analysis. These enhancements support our findings of an
anomaly in 2022 and highlight that the 0.1-second reaction time
threshold lacks a foundation in formal statistical evidence.
\eds{let's revisit this again after objective 2 analyses are set}
